\section{Introduction}
In this assignment, we applied different machine learning algorithms on three datasets provided by the UCI Machine Learning Repositories \footnote{http://archive.ics.uci.edu/ml/datasets.html}.

In order to run ML algorithms, we create a ML platform using python libraries. SciKit-Learn \footnote{http://scikit-learn.org/} and PyBrain  \footnote{http://pybrain.org/} are two main libraries used in the platform. SciKit-Learn provides a vast variety of techniques for preprocessing, data imputing and ML algorithms. In order to fill the lack of Neural Network algorithms for supervised learning in SciKit-Learn, we used PyBrain libraries.

The algorithms can be divided in two parts. Main algorithms consisted of \textit{Linear Ridge Regression}, \textit{Nearest Neighbor}, \textit{Support Vector Machine} and \textit{Stochastic Gradient Descent} which are applied on  all databases. Additional algorithms consisted of \textit{Polynomial Ridge Regression}, \textit{Neural Networks}, \textit{Linear Bayesian Ridge Regression} and \textit{Linear Ridge Regression Cross Validation} which are used experimentally on some datasets.

In the following, first we describe applied algorithms and their specifications. Then in three chapters, we explain our experiments and results with every dataset. Each chapter has a conclusion part in which we compare achieved results related to that dataset. At the end, we compare the best results of datasets and propose the most appropriate algorithm for each one.
